{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-03-26 FH Optimality Conditions Paper.tex
physical interpretation

\documentclass[preprint]{elsarticle}
\usepackage{graphics, euscript, float,blkarray, listings}
\usepackage {graphicx}
\usepackage[top = 1 in, bottom = 1 in, right = 1 in, left = 1 in]{geometry}
\usepackage{tabularx, booktabs, array, float, framed}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\usepackage{appendix, setspace}
\usepackage{mathtools}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,thmtools,etoolbox}
\usepackage{algorithm,algorithmicx,algpseudocode}
\usepackage{booktabs,subcaption}
\usepackage{tikz,pgfplots}%\pgfplotsset{compat=1.14}
\pgfplotsset{compat=newest}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage[colorlinks,citecolor=black]{hyperref}
\usepackage{cleveref}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{multicol}
\usepackage[font={large}]{caption}
\usepackage{subcaption}
\usepackage{natbib}

@@

% Theorem definitions
\newtheorem{theorem}{Theorem}[section]
\crefname{theorem}{theorem}{theorems}
\Crefname{theorem}{Theorem}{Theorems}

\newtheorem{prop}[theorem]{Proposition}
\crefname{prop}{proposition}{propositions}
\Crefname{prop}{Proposition}{Propositions}

\newtheorem{lemma}[theorem]{Lemma}
\crefname{lemma}{lemma}{lemmas}
\Crefname{lemma}{Lemma}{Lemmas}

\newtheorem{corollary}[theorem]{Corollary}
\crefname{corollary}{corollary}{corollaries}
\Crefname{corollary}{Corollary}{Corollaries}

%\theoremstyle{remark}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\AtEndEnvironment{remark}{\hfill\ensuremath{\diamondsuit}}
\crefname{remark}{remark}{remarks}
\Crefname{remark}{Remark}{Remarks}

\theoremstyle{definition}
\newtheorem{defn}[theorem]{Definition}
\crefname{defn}{definition}{definitions}
\Crefname{defn}{Definition}{Definitions}

\newtheorem{example}[theorem]{Example}
\AtEndEnvironment{example}{\hfill\ensuremath{\bigcirc}}
\crefname{example}{example}{example}
\Crefname{example}{Example}{Examples}

@@

\newcommand{\e}[1]{\mathrm{e}^{#1}}
\newcommand{\goyal}{GR}

@@

\biboptions{numbers,sort&compress}

@@

\begin{frontmatter}
\title{ {$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\tnoteref{mytitlenote}}}
\author{Klajdi Sinani$^*$}
\ead{klajdi@vt.edu}
\cortext[cor1]{Corresponding author}

\author{Serkan~Gugercin}
\ead{gugercin@vt.edu}

\tnotetext[mytitlenote]{This work was funded by the U.S. National Science Foundation under grants DMS-1522616 and  DMS-1720257.}

\address{Department of Mathematics, Virginia Polytechnic Institute and State University, Blacksburg, VA 24061, USA}

@@

Consider the linear time-invariant dynamical system:
\begin{equation}  \label{fom1}
\begin{array}{rcl}
\dot{\x}(t) & =& \A\x(t) +\B\uu(t)\\
\y(t)&=&\C\x(t) 
\end{array}
~~\mbox{with}~~ \x(0) = \mathbf{0},
\quad \Longleftrightarrow \quad
\y(t)=\int_{0}^{t}\h (t-\tau)\uu(\tau) d\tau,
\end{equation}
\noindent
where $\A \in \R^{n\times n}$, $\B\in \R^{n\times m}$, and $\C\in \R^{p\times n}$ are constant matrices; 
the variable $\x(t)\in \R^n$ denotes the internal variables, $\uu(t)\in \R^m$ denotes the control inputs, and $\y(t)\in \R^p$ denotes the outputs; and $\h(t)=\C e^{\A t}\B$ is the impulse response of the full model.   The length of the internal variable $\x(t)$, i.e., $n$, is called the order of the full model that we would like to reduce.  Model
reduction achieves this by replacing the original model with a lower dimensional one:

\begin{equation}  \label{rom1}
\begin{array}{rcl}
\dot{\x}_r(t) & =& \A_r\x_r(t) +\B_r\uu(t)\\
\y_r(t)&=&\C_r\x_r(t) 
\end{array}
~~\mbox{with}~~ \x_r(0) = \mathbf{0},
\quad \Longleftrightarrow \quad
\y_r(t)=\int_{0}^{t}\h_r (t-\tau)\uu(\tau) d\tau,
\end{equation}
where as in \eqref{fom1}, $\h_r(t)=\C_r e^{\A_r t}\B_r$ is the impulse response of the reduced model, and $\A_r \in \R^{r\times r}$, $\B_r\in \R^{r\times m}$, and $\C_r\in \R^{p\times r}$ with $r\ll n$. The goal is that the output of the reduced model, $\y_r(t)$, approximates the true output, $\y(t)$, of the original system accurately in an appropriate norm.

@@

%Error Measures
\section{$\ch_2$-Optimal Model Reduction: The Infinite Horizon Case} \label{sec:intro}
Model reduction with respect to the $\ch_2$ norm in the infinite horizon case has been studied extensively; see, for examples, \cite{BarCO91, BryC90, FulO90, MeiL67, Hal92, HylB85, SpaMM92, YanL99, LepMPV91, GugBA08,AniBGA13,Wil70,vuillemin2014poles,CasL18,panzer2013,gerstner2007hom,VanGA08, breiten2013near} and the references therein. 
In this section, we briefly recall these results as they will help to highlight the similarities to and differences from the finite-horizon case that we are interested in.
\subsection{$\ch_2$ Norm and $\ch_2$ Error Measure}
The error analysis for model reduction of linear dynamical systems can be conducted either in the frequency domain or in the time domain. Therefore, we define the $\ch_2$ norm in each domain. 
\begin{Definition}
Let $\h(t)$ and $\g(t)$ be the impulse responses of two asymptotically stable\footnote{We will call
$\h(t) = \C e^{\A t} \B$ asymptotically stable if all the eigenvalues of $\A$ have negative real parts. We will call 
$\h(t)$ stable when $\A$ has some semi-simple eigenvalues on the imaginary axis in addition to those with negative real parts. Otherwise, we call  $\h(t)$ unstable.}
linear dynamical systems with real state-space realizations.
The $\ch_2$ inner product $\langle \cdot, \cdot \rangle_{\ch_2}$ and the $\ch_2$ norm $\| \cdot \|_{\ch_2}$  are 
\begin{align*}
\langle \h, \g \rangle_{\ch_2} =\int_0^\infty \mathsf{Tr}\left((\h(t))^T \g(t)\right) dt \quad \mbox{and}\quad \norm{\h}_{\ch_2}= \sqrt{ \int_0^\infty \norm{\h}_F^2 dt },
\end{align*} 
respectively, where $ \mathsf{Tr}(\cdot)$ denotes the trace and $\norm{\cdot}_F$ denotes the Frobenius norm of a matrix.
\end{Definition}
To define the $\ch_2$ norm in the frequency domain, let $\Y(s)$, $\U(s)$, and $\HH(s)$ denote the Laplace transforms of 
 the output $\y(t)$, the input $\uu(t)$, and the impulse response $\h(t) = \C e^{\A t}\B$
in \eqref{fom1}. Then, taking the Laplace transform of the convolution integral in  \eqref{fom1}, we obtain

@@

Let  $\h (t)= \sum_{j=1}^n e^{\rho_jt} \cc_j \bb_j^T $ and $\h_r(t) = \sum_{i=1}^r e^{\lambda_it}\lc_i  \rc_i^T $ be, respectively, the impulse responses of the full and reduced models  as described in \eqref{eqn:hfull} and \eqref{kernel2}.
Then,
\begin{align} \label{eqn:hhr}
\langle\h, \h_r\rangle_{\ch_2({\tf})}=\sum_{j=1}^n\sum_{i=1}^r\lc_{i}^T\cc_j\bb_j^T\rc_{i}\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j}.
\end{align}
and
\begin{align} \label{eqn:hrhr}
\norm{\h_r}_{\ch_2({\tf})}^2= \sum_{i=1}^r\sum_{j=1}^r\lc_{i}^T\lc_{j}\rc_{j}^T\rc_{i}\dfrac{e^{(\lambda_i+\lambda_j){\tf}}-1}{\lambda_i+\lambda_j}.
\end{align}
\end{Lemma}
\begin{proof}
The both results  follow from the definition of the $\ch_2(\tf)$ inner product.  First consider
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr}\left(\int_0^{\tf}\h_r(t)^T\h(t)\, dt\right).
\end{align*}
Plug $\h (t)= \sum_{j=1}^n \cc_j \bb_j^T e^{\rho_jt}$ and $\h_r(t) = \sum_{i=1}^r \lc_i  \rc_i^T e^{\lambda_it}$
into this formula to obtain
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr} \left(\int_0^{\tf}\sum_{i=1}^r(\lc_{i}\rc_{i}^Te^{\lambda_it})^T\sum_{j=1}^n\cc_j\bb_j^Te^{\rho_jt}dt\right) = \mathsf{Tr} \left(\sum_{i=1}^r 
\sum_{j=1}^n 
\rc_{i}\lc_{i}^T\cc_j \bb_j^T \int_0^{\tf}e^{(\lambda_i + \rho_j )t} dt\right)
\end{align*}
Computing the integral and using the fact that $\mathsf{Tr}(\A_1 \A_2) = \mathsf{Tr}(\A_2 \A_1)$  for two matrices $\A_1$ and $\A_2$ of  appropriate sizes,   we obtain
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr}\left(\sum_{j=1}^n\sum_{i=1}^r\rc_{i}\lc_{i}^T\cc_j\bb_j^T\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j}\right)
=\sum_{j=1}^n\sum_{i=1}^r\lc_{i}^T\cc_j\bb_j^T\rc_{i}\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j},
\end{align*}
which proves \eqref{eqn:hhr}. Then, \eqref{eqn:hrhr} follows directly by replacing $\h(t)$ with $\h_r(t)$ in this derivation. 
\end{proof}
For infinite time horizon, Theorem \ref{h2thm} tells us that a locally $\ch_2$ optimal reduced transfer function is a tangential Hermite interpolant of the original transfer function at the mirror images of the reduced poles. We will show that in the finite horizon case, even though Hermite tangential interpolation is still the necessary conditions for optimality,  what is being interpolated and what the interpolant is are different.

@@

%Remark 3.2
\begin{remark}
Before we prove Theorem \ref{mh2opt}, we briefly comment on its implications. In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.
\end{remark}
The following lemma will be used in the proof of  Theorem \ref{mh2opt}.
\begin{Lemma}\label{mgexp}
Let $\G(s)$ and $\G_r(s)$ be as defined in \eqref{eqn:defG} and \eqref{eqn:defGr}, respectively. Then,
\begin{align}
\G(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j},
\label{eqn:Gatlk}\\
 \G'(-\lambda_k)& =-\sum_{j=1}^n\cc_i\bb_i^T\dfrac {{\tf} (\lambda_k+\rho_j)e^{(\lambda_k+\rho_j){\tf}}+e^{(\lambda_k+\rho_j){\tf}}+1}{(\lambda_k+\rho_j)^2}, \label{eqn:Gpatlk}  \\
 \G_r(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\lc_j\rc_j^T\dfrac{e^{(\lambda_k+\lambda_j){\tf}}-1}{\lambda_k+\lambda_j}, ~~\mbox{and} 
\label{eqn:Gratlk}\\
 \G_r'(-\lambda_k)& =-\sum_{j=1}^n\lc_j\rc_j^T\dfrac {{\tf} (\lambda_k+\lambda_j)e^{(\lambda_k+\lambda_i){\tf}}+e^{(\lambda_k+\lambda_i){\tf}}+1}{(\lambda_k+\lambda_j)^2}. \label{eqn:Grpatlk} 
\end{align}
\end{Lemma}
\begin{proof}
Recall the definition of $\G(s) = -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)$. Note that we assume that the eigenvalues of $\A$ are simple. Therefore, $e^{\A \tf}$ is also diagonalizable by the eigenvectors of $\A$. Using this fact and the pole-zero residue decomposition of   $\HH(s) = \C(s\I-\A)^{-1} \B = \sum_{j=1}^n \frac{\cc_j \bb_j^T}{s-\rho_j}$, we obtain 
\begin{align}
\G(s) &= -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)  \nonumber \\ 
&=-e^{-s{\tf}}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{\rho_j\tf}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j}
=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{-e^{(-s + \rho_j){\tf}}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j} \nonumber\\
&=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(-s+\rho_j)\tf}-1}{-s+\rho_j}. \label{eq:Gs}
\end{align}
Thus,
\begin{align*}
\G(-\lambda_k)=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j},
\end{align*}
which proves \eqref{eqn:Gatlk}. To prove \eqref{eqn:Gpatlk}, we first differentiate \eqref{eq:Gs} with respect to $s$ to obtain
 \begin{align*}
 \G'(s) =\sum_{j=1}^n\cc_j\bb_j^T\dfrac {{\tf} (s-\rho_j)e^{(-s+\rho_j){\tf}}+e^{(-s+\rho_j){\tf}}-1}{(s-\rho_j)^2}
 \end{align*}
 Plugging in $s= -\lambda_k$ in this last expression yields the desired result \eqref{eqn:Gpatlk}. The proofs of
 \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk} follow analogously. 
\end{proof}

@@

\begin{remark}
{\color{red} In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.}
\end{remark}

>>>>

%\documentclass[preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\usepackage{graphics, euscript, float,blkarray, listings}
\usepackage {graphicx}
%\usepackage[top = 1 in, bottom = 1 in, right = 1 in, left = 1 in]{geometry}
\usepackage{tabularx, booktabs, array, float, framed}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\usepackage{appendix, setspace}
\usepackage{mathtools}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{mathtools,thmtools,etoolbox}
\usepackage{algorithm,algorithmicx,algpseudocode}
\usepackage{booktabs,subcaption}
\usepackage{tikz,pgfplots}%\pgfplotsset{compat=1.14}
\pgfplotsset{compat=newest}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage[colorlinks,citecolor=black]{hyperref}
%\usepackage{cleveref}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{multicol}
\usepackage[font={large}]{caption}
\usepackage{subcaption}
%\usepackage{natbib}

@@

% Theorem definitions
\newtheorem{theorem}{Theorem}[section]
%\crefname{theorem}{theorem}{theorems}
%\Crefname{theorem}{Theorem}{Theorems}

%\newtheorem{prop}[theorem]{Proposition}
%\crefname{prop}{proposition}{propositions}
%\Crefname{prop}{Proposition}{Propositions}

\newtheorem{lemma}[theorem]{Lemma}
%\crefname{lemma}{lemma}{lemmas}
%\Crefname{lemma}{Lemma}{Lemmas}

\newtheorem{corollary}[theorem]{Corollary}
%\crefname{corollary}{corollary}{corollaries}
%\Crefname{corollary}{Corollary}{Corollaries}

\theoremstyle{remark}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\AtEndEnvironment{remark}{\hfill\ensuremath{\diamondsuit}}
%\crefname{remark}{remark}{remarks}
%\Crefname{remark}{Remark}{Remarks}
%
%\theoremstyle{definition}
%\newtheorem{defn}[theorem]{Definition}
%\crefname{defn}{definition}{definitions}
%\Crefname{defn}{Definition}{Definitions}

\newtheorem{example}[theorem]{Example}
\AtEndEnvironment{example}{\hfill\ensuremath{\bigcirc}}
%\crefname{example}{example}{example}
%\Crefname{example}{Example}{Examples}

@@

%\newcommand{\e}[1]{\mathrm{e}^{#1}}
\newcommand{\goyal}{GR}

@@

%\biboptions{numbers,sort&compress}

@@

\begin{frontmatter}
\title{ {$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}} }
\author{Klajdi Sinani\thanksref{cor}} \ead{klajdi@vt.edu},
\author{Serkan~Gugercin} \ead{gugercin@vt.edu}

\thanks[mytitlenote]{This work was funded by the U.S. National Science Foundation under grants DMS-1522616 and  DMS-1720257.}
\thanks[cor]{Corresponding author }
\address{Department of Mathematics, Virginia Polytechnic Institute and State University, Blacksburg, VA 24061, USA}

@@

Consider the linear time-invariant dynamical system:
\begin{equation}  \label{fom1}
\begin{array}{rcl}
\dot{\x}(t) & =& \A\x(t) +\B\uu(t)\\
\y(t)&=&\C\x(t) 
\end{array}
%~~\mbox{with}~~ \x(0) = \mathbf{0},
\; \Leftrightarrow \;
\y(t)=\int_{0}^{t}\h (t-\tau)\uu(\tau) d\tau,
\end{equation}
\noindent
where $  \x(0) = \mathbf{0}, \A \in \R^{n\times n}$, $\B\in \R^{n\times m}$, and $\C\in \R^{p\times n}$ are constant matrices; 
the variable $\x(t)\in \R^n$ denotes the internal variables, $\uu(t)\in \R^m$ denotes the control inputs, and $\y(t)\in \R^p$ denotes the outputs; and $\h(t)=\C e^{\A t}\B$ is the impulse response of the full model.   The length of the internal variable $\x(t)$, i.e., $n$, is called the order of the full model that we would like to reduce.  Model
reduction achieves this by replacing the original model with a lower dimensional one:
\begin{equation}  \label{rom1}
\begin{array}{rcl}
\dot{\x}_r(t) & =& \A_r\x_r(t) +\B_r\uu(t)\\
\y_r(t)&=&\C_r\x_r(t) 
\end{array}
%~~\mbox{with}~~ \x_r(0) = \mathbf{0},
\; \Leftrightarrow \;
\y_r(t)=\int_{0}^{t}\h_r (t-\tau)\uu(\tau) d\tau,
\end{equation}
where as in \eqref{fom1}, $\x_r(0) = \mathbf{0}, \h_r(t)=\C_r e^{\A_r t}\B_r$ is the impulse response of the reduced model, and $\A_r \in \R^{r\times r}$, $\B_r\in \R^{r\times m}$, and $\C_r\in \R^{p\times r}$ with $r\ll n$. The goal is that the output of the reduced model, $\y_r(t)$, approximates the true output, $\y(t)$, of the original system accurately in an appropriate norm.

@@

%Error Measures
\section{$\ch_2$-Optimal Model Reduction: The Infinite Horizon Case} \label{sec:intro}
Model reduction with respect to the $\ch_2$ norm in the infinite horizon case has been studied extensively; see, for examples, \cite{BarCO91, BryC90 , FulO90, MeiL67, Hal92, HylB85, SpaMM92, YanL99, LepMPV91, GugBA08,AniBGA13,Wil70, vuillemin2014poles,CasL18, panzer2013, gerstner2007hom, VanGA08, breiten2013near} and the references therein. 
In this section, we briefly recall these results as they will help to highlight the similarities to and differences from the finite-horizon case that we are interested in.
\subsection{$\ch_2$ Norm and $\ch_2$ Error Measure}
The error analysis for model reduction of linear dynamical systems can be conducted either in the frequency domain or in the time domain. Therefore, we define the $\ch_2$ norm in each domain. 
\begin{Definition}
Let $\h(t)$ and $\g(t)$ be the impulse responses of two asymptotically stable\footnote{We will call
$\h(t) = \C e^{\A t} \B$ asymptotically stable if all the eigenvalues of $\A$ have negative real parts. We will call 
$\h(t)$ stable when $\A$ has some semi-simple eigenvalues on the imaginary axis in addition to those with negative real parts. Otherwise, we call  $\h(t)$ unstable.}
linear dynamical systems with real state-space realizations.
The $\ch_2$ inner product $\langle \cdot, \cdot \rangle_{\ch_2}$ and the $\ch_2$ norm $\| \cdot \|_{\ch_2}$  are 
\begin{align*}
\langle \h, \g \rangle_{\ch_2} =\int_0^\infty \mathsf{Tr}\left((\h(t))^T \g(t)\right) dt \quad \mbox{and}\quad \norm{\h}_{\ch_2}= \sqrt{ \int_0^\infty \norm{\h}_F^2 dt },
\end{align*} 
respectively, where $ \mathsf{Tr}(\cdot)$ denotes the trace and $\norm{\cdot}_F$ denotes the Frobenius norm of a matrix.
\end{Definition}
To define the $\ch_2$ norm in the frequency domain, let $\Y(s)$, $\U(s)$, and $\HH(s)$ denote the Laplace transforms of 
 the output $\y(t)$, the input $\uu(t)$, and the impulse response $\h(t) = \C e^{\A t}\B$
in \eqref{fom1}. Then, taking the Laplace transform of the convolution integral in  \eqref{fom1}, we obtain

@@

Let  $\h (t)= \sum_{j=1}^n e^{\rho_jt} \cc_j \bb_j^T $ and $\h_r(t) = \sum_{i=1}^r e^{\lambda_it}\lc_i  \rc_i^T $ be, respectively, the impulse responses of the full and reduced models  as described in \eqref{eqn:hfull} and \eqref{kernel2}.
Then,
\begin{align} \label{eqn:hhr}
\langle\h, \h_r\rangle_{\ch_2({\tf})}=\sum_{j=1}^n\sum_{i=1}^r\lc_{i}^T\cc_j\bb_j^T\rc_{i}\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j}.
\end{align}
and
\begin{align} \label{eqn:hrhr}
\norm{\h_r}_{\ch_2({\tf})}^2= \sum_{i=1}^r\sum_{j=1}^r\lc_{i}^T\lc_{j}\rc_{j}^T\rc_{i}\dfrac{e^{(\lambda_i+\lambda_j){\tf}}-1}{\lambda_i+\lambda_j}.
\end{align}
\end{Lemma}
\begin{pf}
The both results  follow from the definition of the $\ch_2(\tf)$ inner product.  First consider
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr}\left(\int_0^{\tf}\h_r(t)^T\h(t)\, dt\right).
\end{align*}
Plug $\h (t)= \sum_{j=1}^n \cc_j \bb_j^T e^{\rho_jt}$ and $\h_r(t) = \sum_{i=1}^r \lc_i  \rc_i^T e^{\lambda_it}$
into this formula to obtain
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr} \left(\int_0^{\tf}\sum_{i=1}^r(\lc_{i}\rc_{i}^Te^{\lambda_it})^T\sum_{j=1}^n\cc_j\bb_j^Te^{\rho_jt}dt\right) = \mathsf{Tr} \left(\sum_{i=1}^r 
\sum_{j=1}^n 
\rc_{i}\lc_{i}^T\cc_j \bb_j^T \int_0^{\tf}e^{(\lambda_i + \rho_j )t} dt\right)
\end{align*}
Computing the integral and using the fact that $\mathsf{Tr}(\A_1 \A_2) = \mathsf{Tr}(\A_2 \A_1)$  for two matrices $\A_1$ and $\A_2$ of  appropriate sizes,   we obtain
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr}\left(\sum_{j=1}^n\sum_{i=1}^r\rc_{i}\lc_{i}^T\cc_j\bb_j^T\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j}\right)
=\sum_{j=1}^n\sum_{i=1}^r\lc_{i}^T\cc_j\bb_j^T\rc_{i}\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j},
\end{align*}
which proves \eqref{eqn:hhr}. Then, \eqref{eqn:hrhr} follows directly by replacing $\h(t)$ with $\h_r(t)$ in this derivation. 
\end{pf}
For infinite time horizon, Theorem \ref{h2thm} tells us that a locally $\ch_2$ optimal reduced transfer function is a tangential Hermite interpolant of the original transfer function at the mirror images of the reduced poles. We will show that in the finite horizon case, even though Hermite tangential interpolation is still the necessary conditions for optimality,  what is being interpolated and what the interpolant is are different.

@@

%Remark 3.2
\begin{remark}
Before we prove Theorem \ref{mh2opt}, we briefly comment on its implications. In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.
\end{remark}
The following lemma will be used in the proof of  Theorem \ref{mh2opt}.
\begin{Lemma}\label{mgexp}
Let $\G(s)$ and $\G_r(s)$ be as defined in \eqref{eqn:defG} and \eqref{eqn:defGr}, respectively. Then,
\begin{align}
\G(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j},
\label{eqn:Gatlk}\\
 \G'(-\lambda_k)& =-\sum_{j=1}^n\cc_i\bb_i^T\dfrac {{\tf} (\lambda_k+\rho_j)e^{(\lambda_k+\rho_j){\tf}}+e^{(\lambda_k+\rho_j){\tf}}+1}{(\lambda_k+\rho_j)^2}, \label{eqn:Gpatlk}  \\
 \G_r(-\lambda_k)&=\phantom{-}\sum_{j=1}^n\lc_j\rc_j^T\dfrac{e^{(\lambda_k+\lambda_j){\tf}}-1}{\lambda_k+\lambda_j}, ~~\mbox{and} 
\label{eqn:Gratlk}\\
 \G_r'(-\lambda_k)& =-\sum_{j=1}^n\lc_j\rc_j^T\dfrac {{\tf} (\lambda_k+\lambda_j)e^{(\lambda_k+\lambda_i){\tf}}+e^{(\lambda_k+\lambda_i){\tf}}+1}{(\lambda_k+\lambda_j)^2}. \label{eqn:Grpatlk} 
\end{align}
\end{Lemma}
\begin{pf}
Recall the definition of $\G(s) = -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)$. Note that we assume that the eigenvalues of $\A$ are simple. Therefore, $e^{\A \tf}$ is also diagonalizable by the eigenvectors of $\A$. Using this fact and the pole-zero residue decomposition of   $\HH(s) = \C(s\I-\A)^{-1} \B = \sum_{j=1}^n \frac{\cc_j \bb_j^T}{s-\rho_j}$, we obtain 
\begin{align}
\G(s) &= -e^{-s\tf}\C(s\I-\A)^{-1}e^{\A \tf}\B+\HH(s)  \nonumber \\ 
&=-e^{-s{\tf}}\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{\rho_j\tf}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j}
=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{-e^{(-s + \rho_j){\tf}}}{s-\rho_j}+\sum_{j=1}^n\cc_j\bb_j^T\dfrac{1}{s-\rho_j} \nonumber\\
&=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(-s+\rho_j)\tf}-1}{-s+\rho_j}. \label{eq:Gs}
\end{align}
Thus,
\begin{align*}
\G(-\lambda_k)=\sum_{j=1}^n\cc_j\bb_j^T\dfrac{e^{(\lambda_k+\rho_j){\tf}}-1}{\lambda_k+\rho_j},
\end{align*}
which proves \eqref{eqn:Gatlk}. To prove \eqref{eqn:Gpatlk}, we first differentiate \eqref{eq:Gs} with respect to $s$ to obtain
 \begin{align*}
 \G'(s) =\sum_{j=1}^n\cc_j\bb_j^T\dfrac {{\tf} (s-\rho_j)e^{(-s+\rho_j){\tf}}+e^{(-s+\rho_j){\tf}}-1}{(s-\rho_j)^2}
 \end{align*}
 Plugging in $s= -\lambda_k$ in this last expression yields the desired result \eqref{eqn:Gpatlk}. The proofs of
 \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk} follow analogously. 
\end{pf}

@@

%Remark
\begin{remark}
{\color{red} In the infinite-horizon case, if  $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$. The interpolation of $\G(s)$ guarantees that we are approximating the model on the finite horizon. For instance, consider the inverse Laplace transform of $\G(s)$:
\begin{align*}
\mathcal{L}^{-1}\{\G(s)\}&=\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i {\tf}}e^{\lambda_i (t-{\tf})}\\
&=\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i t}
\end{align*}
where $u_{\tf}(t)$ is the unit step function
\begin{align*}
u_{\tf}(t)=
 \begin{cases} 
      1 &    t\leq {\tf} \\    
      0 &    t > {\tf} 
   \end{cases}.
\end{align*}
In other words, if we were to use an $\ch_2$ optimal algorithm on $\G(s)$, we would be approximating a finite horizon model by an infinite horizon one. For this reason, the interpolation of $\G(s)$ by $\G_r(s)$ is necessary. 
However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.}
\end{remark}
